Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-19 paper/ms.tex
Small updates to intro

We show the time evolution of different bar properties in Fig.~\ref{fig:prop}.
In the upper panel, we show the pattern speed over time in the N-body (blue)
and SMUGGLE (orange) runs. The pattern speed in the N-body case slows down
while the pattern speed in the SMUGGLE case remains constant. The slowing down
of the pattern speed in the N-body case is consistent with a long line of
numerical research on bars in N-body simulations\cite{1992ApJ...400...80H,
2000ApJ...543..704D, 2002MNRAS.330...35A, 2002ApJ...569L..83A,
2003MNRAS.341.1179A, 2003MNRAS.346..251O, 2005MNRAS.363..991H,
2006ApJ...637..214M, 2007MNRAS.375..460W, 2009ApJ...697..293D}. However, in
the SMUGGLE case the pattern speed remains constant. After the first Gyr of
evolution, we find that the pattern speed increases by only $\sim10\%$ over
the next $4\,\textrm{Gyr}$, compared to a $\sim43\%$ decrease in the pattern
speed for the N-body run over the same interval. As we saw
qualitatively in Fig.~\ref{fig:overview}, the length of the bar in the N-body
case grows over time while it remains constant in the SMUGGLE case.

>>>>

We show the time evolution of different bar properties in Fig.~\ref{fig:prop}.
In the upper panel, we show the pattern speed over time in the N-body (blue)
and SMUGGLE (orange) runs. The pattern speed in the N-body case slows down
while the pattern speed in the SMUGGLE case remains constant. The slowing down
of the pattern speed in the N-body case is consistent with a long line of
numerical research on bars in N-body simulations.\cite{1992ApJ...400...80H,
2000ApJ...543..704D, 2002MNRAS.330...35A, 2002ApJ...569L..83A,
2003MNRAS.341.1179A, 2003MNRAS.346..251O, 2005MNRAS.363..991H,
2006ApJ...637..214M, 2007MNRAS.375..460W, 2009ApJ...697..293D} However, in the
SMUGGLE case the pattern speed remains constant. After the first Gyr of
evolution, we find that the pattern speed increases by only $\sim10\%$ over
the next $4\,\textrm{Gyr}$, compared to a $\sim43\%$ decrease in the pattern
speed for the N-body run over the same interval. As we saw qualitatively in
Fig.~\ref{fig:overview}, the length of the bar in the N-body case grows over
time while it remains constant in the SMUGGLE case. This is also consistent
with previous numerical work, which found that bars tend to grow as they slow
down and the radius of corotation increases.\cite{2000ApJ...543..704D,
2003MNRAS.341.1179A}
